### 2019-08-08 paper/paper.tex
add external lib sample

\textbf{TSML} is a package for time series data processing, classification, and prediction. 
It provides common API for ML libraries from Python's ScikitLearn, 
R's caret, and native Julia MLs for seamless integration of heterogenous 
libraries to create complex ensembles for robust time-series prediction, clustering, and classification.
TSML has the following features:
\begin{itemize}
\item data type clustering/classification for automatic data discovery
\item aggregation based on date/time interval
\item imputation based on symmetric Nearest Neighbors
\item statistical metrics for data quality assessment
\item ML wrapper with more than 100+ libraries from caret, scikitlearn, and julia
\item date/value matrix conversion of 1-D time series using sliding windows for ML input
\item pipeline API for high-level description of the processing workflow
\item specific cleaning/normalization workflow based on data type
\item automatic selection of optimised ML model
\item automatic segmentation of time-series data into matrix form for ML training and prediction 
\item extensible architecture using just two main interfaces: fit and transform
\item meta-ensembles for automatic feature and model selection
\item support for distributed computation for scalability and speed
\end{itemize}

@@

There are cases however where the main task of time series classification 
requires more complex ensemble model using hierarchy or trees where 
members are from heterogenous ML libraries. For illustration purposes, we
will show how to ensemble ML libraries from ScikitLearn and Caret from Julia
meta-ensembles that support common \emph{fit} and \emph{transform} APIs.

>>>>

\textbf{TSML} is a package for time series data processing, classification, and prediction. 
It provides common API for ML libraries from Python's ScikitLearn, 
R's caret, and native Julia MLs for seamless integration of heterogeneous 
libraries to create complex ensembles for robust time-series prediction, clustering, and classification.
TSML has the following features:
\begin{itemize}
\item data type clustering/classification for automatic data discovery
\item aggregation based on date/time interval
\item imputation based on symmetric Nearest Neighbors
\item statistical metrics for data quality assessment
\item ML wrapper with more than 100+ libraries from caret, scikitlearn, and julia
\item date/value matrix conversion of 1-D time series using sliding windows for ML input
\item pipeline API for high-level description of the processing workflow
\item specific cleaning/normalization workflow based on data type
\item automatic selection of optimised ML model
\item automatic segmentation of time-series data into matrix form for ML training and prediction 
\item extensible architecture using just two main interfaces: fit and transform
\item meta-ensembles for automatic feature and model selection
\item support for distributed computation for scalability and speed
\end{itemize}

@@

There are cases however where the main task of time series classification 
requires more complex ensemble model using hierarchy or tree where 
members are composed of heterogeneous ML learners from binaries in 
different languages. For illustration purposes, we will show how to 
ensemble ML libraries from ScikitLearn and Caret using \textbf{TSML} 
meta-ensembles that support the \emph{fit} and \emph{transform} APIs.

Load necessary modules:
\begin{lstlisting}[language = Julia]
@everywhere using TSML, TSMLextra, Plots
@everywhere using TSML.TSMLTypes
@everywhere using TSML: TSClassifier
@everywhere using TSML.TSClassifiers.FileStats
@everywhere using TSML.TSMLTransformers
@everywhere using TSML.EnsembleMethods
@everywhere using TSML.DecisionTreeLearners
@everywhere using TSML.Utils
@everywhere using TSMLextra.CaretLearners
@everywhere using TSMLextra.SKLearners
@everywhere using TSML.MLBaseWrapper

@everywhere using DataFrames
@everywhere using Random
@everywhere using Statistics
@everywhere using StatsBase: iqr
@everywhere using RDatasets
\end{lstlisting}

Setup external learners:
\begin{lstlisting}[language = Julia]
# Caret ML
@everywhere caret_svmlinear = 
   CaretLearner(Dict(:learner=>"svmLinear"))
@everywhere caret_treebag = 
   CaretLearner(Dict(:learner=>"treebag"))
@everywhere caret_rpart = 
   CaretLearner(Dict(:learner=>"rpart"))
@everywhere caret_rf = 
   CaretLearner(Dict(:learner=>"rf"))

# ScikitLearn ML
@everywhere sk_ridge = 
   SKLearner(Dict(:learner=>"RidgeClassifier"))
@everywhere sk_sgd = 
   SKLearner(Dict(:learner=>"SGDClassifier"))
@everywhere sk_knn = 
   SKLearner(Dict(:learner=>"KNeighborsClassifier"))
@everywhere sk_gb = 
   SKLearner(Dict(:learner=>
   "GradientBoostingClassifier",
   :impl_args=>Dict(:n_estimators=>10)))
@everywhere sk_extratree = 
   SKLearner(Dict(:learner=>"ExtraTreesClassifier",
   :impl_args=>Dict(:n_estimators=>10)))
@everywhere sk_rf = 
   SKLearner(Dict(:learner=>
   "RandomForestClassifier",
   :impl_args=>Dict(:n_estimators=>10)))
\end{lstlisting}

Setup Julia learners and meta-ensembles:
\begin{lstlisting}[language = Julia]
# Julia ML
@everywhere jrf = RandomForest()
@everywhere jpt = PrunedTree()
@everywhere jada = Adaboost()

# Julia Ensembles
@everywhere jvote_ens=VoteEnsemble(Dict(
   :learners=>[jrf,jpt,sk_gb,sk_extratree,sk_rf]))
@everywhere jstack_ens=StackEnsemble(Dict(
   :learners=>[jrf,jpt,sk_gb,sk_extratree,sk_rf]))
@everywhere jbest_ens=BestLearner(Dict(
   :learners=>[jrf,sk_gb,sk_rf]))
@everywhere jsuper_ens=VoteEnsemble(Dict(
   :learners=>[jvote_ens,jstack_ens,
               jbest_ens,sk_rf,sk_gb]))
\end{lstlisting}
